Title Goes Here

### 2020-05-05 analysis/paper/paper.Rmd
add mean cv lines

```{r}
# plot CVs by site with number of artefacts showing >10
# phase 2 and phase 3 sites only
cv_by_site_df_label_more_than_10 <- 
df_sitename %>% 
  unite(col = "site_phase", 
        c(sitename, 
          SPstage.Stage), 
        sep = "_") %>% 
  group_by(site_phase) %>% 
  add_tally() %>% 
  filter( n > 10) %>% 
   mutate(label = as.factor(paste0(site_phase,' (N = ', n, ")"))) %>%   select(-n) %>% 
 nest(-site_phase, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv))) %>% 
  unnest(cv_by_site) %>% 
  select(-data)

@@

cv_by_site_df_label_more_than_10 %>%
  pivot_longer(cols = -c(site_phase, label), 
               names_to = "lithic_attribute",
               values_to = "CV") %>%
  filter(lithic_attribute %in% c("ML", "MW", "TW")) %>%

  ggplot(aes(x = lithic_attribute, 
             y = CV)) +
  geom_col() +
  facet_wrap(~  label) +
  ggtitle("CVs of point attributes by site (with sites >10 artefacts)") +
  theme_minimal()
```

>>>>

```{r}
# plot CVs by site with number of artefacts showing >10
# phase 2 and phase 3 sites only
cv_by_site_df_label_more_than_10 <- 
df_sitename %>% 
  unite(col = "site_phase", 
        c(sitename, 
          SPstage.Stage), 
        sep = "_") %>% 
  group_by(site_phase) %>% 
  add_tally() %>% 
  filter( n > 5) %>% 
   mutate(label = as.factor(paste0(site_phase,' (N = ', n, ")"))) %>%   select(-n) %>% 
 nest(-site_phase, -label) %>% 
  mutate(cv_by_site = map(data, ~map_df(.x, cv))) %>% 
  unnest(cv_by_site) %>% 
  select(-data)

@@

cv_by_site_df_label_more_than_10_ml_mw_tw <- 
cv_by_site_df_label_more_than_10 %>%
  pivot_longer(cols = -c(site_phase, label), 
               names_to = "lithic_attribute",
               values_to = "CV") %>%
  filter(lithic_attribute %in% c("ML", "MW", "TW"))  %>% 
  mutate(phase = parse_number(str_extract(site_phase, "_."))) %>% 
  group_by(site_phase) %>% 
  mutate(mean_cv = mean(CV))

  ggplot(cv_by_site_df_label_more_than_10_ml_mw_tw,
         aes(x = lithic_attribute, 
             y = CV)) +
  geom_col() +
  geom_hline(aes(yintercept = mean_cv), 
             colour = "red") +
  facet_wrap(~  label) +
  ggtitle("CVs of point attributes by site (with sites >10 artefacts)") +
  theme_minimal()
```
